### 2018-05-04 papers/synth/related.tex
citations added

In recent years, there has been a wide range of methods
developed for the similar synthesis problems~\cite{sktech,cegis,exampleSynth}.
%
They range from filling gaps an implementation of C programs from the
pool of template predicates to learn learn an a program from example
runs of the program.
%
In the course of developing such methods,
the background technology, i.e. solving of quantified
constraints,~\cite{depQBF,Z3quantifier,markusRabeSolver} has been evolving rapidly.

>>>>

In recent years, there has been a wide range of methods
developed for the similar synthesis problems~\cite{sketch,sygus,exampleSynth}.
%
They range from filling gaps an implementation of C programs from the
pool of template predicates to learn learn an a program from example
runs of the program.
%
In the course of developing such methods,
the background technology, i.e. solving of quantified
constraints,~\cite{lonsing2010depqbf,z3Quant} has been evolving rapidly.
